Ants-Review: an Ethereum-Based Protocol for Incentivized Peer Reviews

### 2020-12-24 article.tex
Prova titolo breve

\title{Ants-Review: an Ethereum-Based Privacy-Oriented Protocol for Incentivized Open Peer Reviews}

@@

Atomic Energy and Alternative Energies Commission (CEA), Frédéric Joliot Institute for Life Sciences, NeuroSpin, UNICOG, INSERM U992, Paris-Saclay, France

@@

\and MakerDAO, Community Development, London, United Kingdom \and
WFIL Labs\\

>>>>

\title{Ants-Review: an Ethereum-Based Protocol for Incentivized Peer Reviews}

@@

Atomic Energy and Alternative Energies Commission (CEA), Frédéric Joliot Institute for Life Sciences, NeuroSpin, Cognitive Neuroimaging Unit, Saclay, France

@@

\and MakerDAO, Community Development, London, United Kingdom \\
